SAT Competition 2020\tnoteref{title}

### 2021-06-22 paper/main.tex
bib revised, please do not screw this up again...

\paragraph{Planning (SAS+)}
We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counterexample-guided abstraction refinement (CEGAR)~\cite{Froleyks:2019:Pasar}.

@@

@@

A further, more recent line of evolution in SAT solvers
is rooted in the \solver{CoMinisatPS} by Oh, which is itself a again a fork of \solver{Minisat}, introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
Building on \solver{CoMinisatPS}, 
The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{Liang:2016:LRB}. 
The at-the-time award-winning variant \solver{MapleCOMSPS} by Liang et al.~implements a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) of \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.

@@

% \subsection{Solver Ranking Robustness}
\subsection{Influence of Benchmark Selection on Solver Ranking}
The main result of the competition is the ranking of the solvers participating
in the Main track, according to their average PAR-2 score. To evaluate the impact
of benchmark selection on the solver ranking, we follow the experiments
described in the tool suite
\texttt{benchfeature}~\cite{benchfeature}.
% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
% by Fazekas, Kaufmann and Biere.
% performed the following
% experiment:

We first use random sampling to select subsets of the benchmarks used in the Main track.
We start with $316$ benchmarks that have been solved by at least one solver in
the Main track and remove a number of benchmarks randomly. For each
possible subset size (1--316) we generate 50 random samples.

The solvers are assigned a new rank in ascending order of their PAR-2 score on
each random sample. Note that we never encounter a tie. This ranking can be
seen as an estimate of the original ranking.
If even relatively small random samples result in a good estimate, we draw a
positive conclusion about the robustness of the ranking.
% We draw a positive conclusion about the robustness of the original ranking, if
% even the resulting estimate from relatively small random samples
% are good approximations.
To determine how similar an estimate is to the original ranking, we calculate
the \emph{Spearman's rank correlation coefficient} of the two rankings.
% and compute the correlation coefficient.

Spearman's rank correlation coefficient
for two rankings $r_{1}$ and $r_{2}$
is defined by the following equation:
% \begin{equation}
% \label{eq-spearman}
\[
    \rho = 1 - \frac{6\cdot\sum_{S}{(r_{1}(S) - r_{2}(S))^2}}{n(n^2-1)},
\]
% \end{equation}
where $n$ is the number of solvers in the Main track ($48$), and the rankings
$r_{\{1,2\}}(S)$ map a solver $S$ to its rank, \emph{i.e.,} $1$ for the best
performing solver, whereas $48$ is assigned to the solver
with the highest average PAR-2 score.

@@

The mean and standard deviation of the computed correlation coefficients are
depicted in Figure~\ref{fig:sampleAll}.
The rank correlation is high even for relatively small samples.
The average rank correlation drops below $0.99$ only after randomly removing at least $95$ benchmarks, which is $30\%$ of the considered benchmark set. Accordingly, removing fewer benchmarks randomly has almost no effect on the ranking of the solvers.
Furthermore, removing fewer than $200$ ($63\%$) benchmarks, still results in an average rank correlation above $0.96$.

This suggests that the impact of the random selection in Algorithm~\ref{algo:select} on the solver ranking is limited.
% \ref{sec:byob}
The collected data cannot show whether all of the benchmarks originally
submitted by the solver authors have a systematic bias. However, since each
newly submitted benchmark family originates from a different domain and is often
the result of current research, we can assume that the submitted families
together are representative.

@@

The 2020 SAT Competition successfully continues the tradition of the SAT Competition series. In 2020, significant advances
in SAT solvers compared to previous years are observed. Some of the more interesting observations on the winning solving 
strategies include the following.
All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As can be seen in the \emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use-case.

@@

In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances was often counter-productive and did not lead to a more balanced overall selection of new instances. 
Moreover, this practice discriminated against authors of purely satisfiable or unsatifiable sets of instances. 
Also the hardness criterion of 10 \solver{Minisat} minutes was higher than the hardness criterion of 1 \solver{Minisat} minute of the BYOB rule. 
In future competitions, we will not balance by \emph{satisfiablity} on the author level, we will be more consistent or clear with our \emph{hardness} criteria, and we will specify what it means for an instance to be counted as \emph{unknown}.

The IPASIR interface facilitates the integration of SAT solvers into incremental applications. 
In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 
This calls for the creation of a more diverse and organized repository of applications for incremental SAT solvers. 
Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

This year the Hack track was organized for hacks of \solver{Glucose 3}. 
In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
The \solver{CaDiCaL-alluip} solver -- which is a modified \solver{CaDiCaL} -- has shown competitive performance in this competitition.

The first instantiation of an Application track has been a Planning track. 
The results show that different solvers take the lead when we only evaluate for a single application. 
We intend to run further instantiations of the Application track. 
In the next competition, we will compile a set of 200 cryptographic benchmark instances for a Crypto track.

The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolios and to stimulate development of new code-bases. 
The rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base. 
Therefore, the \emph{Portfolio rule} will receive some refinement in future competitions.

The results of the \emph{Planning} track as well as our differentiated analysis of the results highlight the individual contributions of many submissions. 
Our plan for the future competitions is to always run a special track for varying applications alongside the Main track.

>>>>

\paragraph{Planning (SAS+)}
We selected $50$ planning instances to evaluate incremental SAT solvers with \textsf{Pasar}, a planner which uses counterexample-guided abstraction refinement (CEGAR)~\cite{Pasar19}.

@@

An overview of the top-10 solvers in each of the competition tracks discussed in the following
is provided in Table~\ref{tab:results}.

@@

A further, more recent line of evolution in SAT solvers
is rooted in the \solver{CoMinisatPS} by Oh, which is itself a again a fork of \solver{Minisat}, introduced three-tier clause-management~\cite{Oh:2015:satunsat}. 
Building on \solver{CoMinisatPS}, 
The SAT solver \solver{Maple} appeared as a series of forks presenting innovative branching heuristics at SAT Competition 2016~\cite{MapleSAT}. 
The at-the-time award-winning variant \solver{MapleCOMSPS} by Liang et al.~implements a hybrid branching heuristic of classic variable-state independent decaying sum (VSIDS)~\cite{Zhang:2001:ClauseLearning} and the newer learning rate based branching (LRB) of \solver{CoMinisatPS}~\cite{Liang:2016:MapleCOMSPS}.

@@

% \subsection{Solver Ranking Robustness}
\subsection{Influence of Benchmark Selection on Solver Ranking}
To evaluate the impact
of benchmark selection on the solver ranking, we follow the experiments
described in the tool suite
\texttt{benchfeature}~\cite{benchfeature}.
% \footnote{\url{http://fmv.jku.at/benchfeature/}} developed
% by Fazekas, Kaufmann and Biere.
% performed the following
% experiment:
In particular, we first use random sampling to select subsets of the benchmarks used in the Main track.
We start with $316$ benchmarks that have been solved by at least one solver in
the Main track and remove a number of benchmarks randomly. For each
possible subset size (1--316) we generate 50 random samples.
The solvers are assigned a new rank in ascending order of their PAR-2 score on
each random sample. Note that we never encounter a tie. This ranking can be
seen as an estimate of the original ranking.
If even relatively small random samples result in a good estimate, we draw a
positive conclusion about the robustness of the ranking.
% We draw a positive conclusion about the robustness of the original ranking, if
% even the resulting estimate from relatively small random samples
% are good approximations.

To determine how similar an estimate is to the original ranking, we calculate
the \emph{Spearman's rank correlation coefficient} of the two rankings.
% and compute the correlation coefficient.
Spearman's rank correlation coefficient
for two rankings $r_{1}$ and $r_{2}$
is defined by the following equation:
% \begin{equation}
% \label{eq-spearman}
\[
    \rho = 1 - \frac{6\cdot\sum_{S}{(r_{1}(S) - r_{2}(S))^2}}{n(n^2-1)},
\]
% \end{equation}
where $n$ is the number of solvers in the Main track ($48$), and the rankings
$r_{\{1,2\}}(S)$ map a solver $S$ to its rank, \emph{i.e.,} $1$ for the best
performing solver, whereas $48$ is assigned to the solver
with the highest average PAR-2 score.

@@

The mean and standard deviation of the computed correlation coefficients are
depicted in Figure~\ref{fig:sampleAll}.
The rank correlation is high even for relatively small samples.
The average rank correlation drops below $0.99$ only after randomly removing at least $95$ benchmarks, which is $30\%$ of the considered benchmark set. Accordingly, removing fewer benchmarks randomly has almost no effect on the ranking of the solvers.
Furthermore, removing fewer than $200$ ($63\%$) benchmarks still results in an average rank correlation above $0.96$.
This suggests that the impact of the random selection in Algorithm~\ref{algo:select} on the solver ranking is limited.
% \ref{sec:byob}
The collected data cannot show whether all of the benchmarks originally
submitted by the solver authors have a systematic bias. However, since each
newly submitted benchmark family originates from a different domain and is often
the result of current research, we can assume that the submitted families
together are representative.

@@

The 2020 SAT Competition successfully continues the tradition of the SAT Competition series. In 2020, significant advances
in SAT solvers compared to previous years were observed. Some of the more interesting observations on the winning solving 
strategies include the following.
All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As observed
from the results of the\emph{Parallel} track, it appears difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$-threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
It appear challenging to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track shows that it is worth integrating a full solver functionality in the incremental use-case.

@@

In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances turned out often counter-productive as it 
did not lead to a more balanced overall selection of new instances. 
Moreover, this practice discriminated against authors who submitted solely satisfiable or unsatisfiable  instances. 
The hardness criterion of 10 \solver{Minisat} minutes was set higher than the hardness criterion of 1 \solver{Minisat} minute of the ``bring your own benchmarks'' rule, 
which can be viewed as problematic. As lessons learned
in future competitions we will not aim balance by satisfiability status on the benchmarks author level. will aim to be more consistent with the imposed \emph{hardness} criteria
for benchmark selection, and will also make sure to clearly communicate what it means for an instance to be counted as \emph{unknown}.

The IPASIR interface facilitates the integration of SAT solvers into incremental applications. 
In contrast to benchmarking with instances given in the 
DIMACS CNF format, there are only few benchmark applications available for the Incremental track.
This calls for more community-level efforts for constructing a more diverse and well-organized repository of applications for incremental SAT solvers. 
Proper benchmarking and new tools for testing incremental SAT solvers may also help solver authors to deal with the more complex use-cases.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

This year the Hack track was organized for hacks of \solver{Glucose 3}. 
In the next competition, we plan on moving to the well structured and documented state-of-the-art SAT solver \solver{CaDiCaL}. 
The \solver{CaDiCaL-alluip} solver---which is a modified \solver{CaDiCaL}---has shown competitive performance in this competitition.

The first instantiation of an Application track was the Planning track organized as a one-time track in 2020.. 
The results show that different solvers take the lead when we only evaluate for a single application, when compared to the overall Main track results.
We intend to run further instantiations of the Application track. 
While essentially none of the solvers that participated in the Planning track seemd particularly optimized for Planning instance, we hope
in future iterations the community will pick up on the challenge of optimizing SAT solvers towards different focus applications, as a complementary
challenge when compared to the generality of the Main track.
In the next competition, the  planned focus of Application track will be on SAT solver applications in cryptology.

The portfolio rule has been established to prohibit participation of pure solver portfolios, in order to stimulate development of new code-bases and
to ensure fair competition among  sequential solvers.
The rule was challenged in this competition as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base. 
We aim to revisit and refine the portfolio rule in future instantiations of the competition in order to ensure that the rule does not unnecessarily hinder interesting 
algorithmic developments in SAT solving.
